Tropical Andes frugivore trait data Frugivoria

### 2025-08-21 code/L0/L0_TropicalAndes_frugivores_frugivoria_traits.Rmd
Changed csv names (previously overrode originals but will see if I can recover them)

```{r}
source("~/GitHub/neotropical_plants/code/data_summary.R")
```

@@

# Write data to csv
```{r}
write.csv(Frugivoria, file = file.path(output_path_L0,"TropicalAndes_Frugivoria_frugivore_traits.csv"))
write.csv(Frugivoria_SpeciesList, file = file.path(output_path_L0,"TropicalAndes_Frugivoria_frugivore_traits_species.csv"))
write.csv(Frugivore_LookupTable, file = file.path(output_path_L1,"TropicalAndes_frugivore_LookupTable.csv"))
```

>>>>

```{r}
source("C:/GitHub_projects/plant-frugivore diversity/neotropical_plants/code/data_summary.R")
```

@@

# Write data to csv
```{r}
write.csv(Frugivoria, file = file.path(output_path_L0,"TropicalAndes_Frugivoria_frugivore_traits_21Aug2025.csv"))
write.csv(Frugivoria_SpeciesList, file = file.path(output_path_L0,"TropicalAndes_Frugivoria_frugivore_traits_species_21Aug2025.csv"))
write.csv(Frugivore_LookupTable, file = file.path(output_path_L1,"TropicalAndes_frugivore_LookupTable_21Aug2025.csv"))
```
